Technical Report

### 2018-04-10 fully-abstract-comp/technical-report.tex
Some more TODOs.

\begin{lemma}
  If
  \begin{itemize}
  \item $\npair{(\var{comp}_1,\var{comp}_1)} \in \lrcomp(W_1)$
  \item $\npair{(\var{comp}_2,\var{comp}_2)} \in \lrcomp(W_2)$
  \end{itemize}
  then
  \begin{itemize}
  \item $\npair{(\var{comp}_1 \bowtie \var{comp}_2,\var{comp}_1\bowtie\var{comp}_2)} \in \lrcomp(W_1\oplus W_2)$.
  \end{itemize}
\end{lemma}

\section{Full Abstraction}
\lau{TODOs from last day in Leuven}
\lau{RESOLVED: components have optional main (pc/data pair)}
\lau{RESOLVED: linking component and context requires only one main (i.e., it is undefined if both or none of the two expose main.)}
\lau{RESOLVED?: Component logical relation. Rough sketch is in white-board-notes/leuven-23-3-2018-3.jpg (top left).}
\dominique{RESOLVED?: Compatibility lemma for linking: if $c_1$ and $c_1'$ are related and $c_2$ and $c_2'$, then so should be $c_1\bowtie c_2$ and $c_1' \bowtie c_2'$ (if defined).}
\lau{TODO: Version of FTLR for programs.}
\lau{TODO: Compatibility lemma for initial executable configuration construct, i.e. a lemma that says ``if two programs are related, then their initial executable configurations will be related''.}
\lau{TODO: A logical relation for executable configurations.}
\lau{TODO: contextual equivalence should be defined in terms of initial executable configuration.}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}
\begin{definition}
  \label{def:points-to-instr}
  A configuration $(\ms,\reg)$ {\sourcecolor or $\Phi = (\ms,\reg,\_,\_)$} is said to point to non-$\scall{}{}{}$ instruction $i$ in $A$ iff
  \[
    \reg(\pcreg) = ((\_,\_),\_,\eaddr,\aaddr) \tand \aaddr \in A
  \]
and
\[
  \decInstr{\ms(\aaddr)} = i
\]
\end{definition}

>>>>

\begin{lemma}[Compatibility lemma for linking]
  If
  \begin{itemize}
  \item $\npair{(\var{comp}_1,\var{comp}_1)} \in \lrcomp(W_1)$
  \item $\npair{(\var{comp}_2,\var{comp}_2)} \in \lrcomp(W_2)$
  \end{itemize}
  then
  \begin{itemize}
  \item $\npair{(\var{comp}_1 \bowtie \var{comp}_2,\var{comp}_1\bowtie\var{comp}_2)} \in \lrcomp(W_1\oplus W_2)$.
  \end{itemize}
\end{lemma}

\subsection{Related execution configurations}
\label{sec:related-exec-confs}

\[
  \lrec(W) = \left\{ \npair{\left(
        \arraycolsep=0pt\array{l}
        (\ms_S,\reg_S,\stk,\ms_\stk),\\
        (\ms_T,\reg_T)\endarray\right)} \middle|
    \begin{array}{l}
      \exists W_M,W_R,W_\pcreg \ldotp W = W_M \oplus W_R \oplus W_\pcreg \tand\\
      \reg_S(\pcreg) = ((\rx,\lin),\baddr,\eaddr,\aaddr) \tand (\trust = \trusted \text{ iff } \aaddr \in \ta) \tand \\
      \npair{( \reg_S(\pcreg),\reg_T(\pcreg) )} \in \lrvg{\trust}(W_\pcreg) \tand \\
      \memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W_M} \tand\\
      \npair{\stpair{\reg}{\reg}} \in \lrrg{\trust}(W_R)
    \end{array}
            \right\}
\]

\begin{lemma}[Compatibility lemma for initial execution configuration construction]
  If
  \begin{itemize}
  \item $\npair{\stpair{\var{comp}}{\var{comp}}} \in \lrcomp(W)$
  \item $\var{comp}_S\rightsquigarrow \Phi_S$
  \item $\var{comp}_T \rightsquigarrow \Phi_T$,
  \end{itemize}
  then
  \begin{itemize}
  \item $\npair{\stpair{\Phi}{\Phi}}\in\lrec(W)$
  \end{itemize}
\end{lemma}

\section{Full Abstraction}
\lau{TODOs from last day in Leuven}
\lau{RESOLVED: components have optional main (pc/data pair)}
\lau{RESOLVED: linking component and context requires only one main (i.e., it is undefined if both or none of the two expose main.)}
\lau{RESOLVED?: Component logical relation. Rough sketch is in white-board-notes/leuven-23-3-2018-3.jpg (top left).}
\dominique{RESOLVED?: Compatibility lemma for linking: if $c_1$ and $c_1'$ are related and $c_2$ and $c_2'$, then so should be $c_1\bowtie c_2$ and $c_1' \bowtie c_2'$ (if defined).}
\lau{TODO: Version of FTLR for programs.}
\lau{RESOLVED: Compatibility lemma for initial executable configuration construct, i.e. a lemma that says ``if two programs are related, then their initial executable configurations will be related''.}
\lau{RESOLVED: A logical relation for executable configurations.}
\lau{RESOLVED: contextual equivalence should be defined in terms of initial executable configuration.}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}
\begin{definition}
  \label{def:points-to-instr}
  A configuration $(\ms,\reg)$ {\sourcecolor or $\Phi = (\ms,\reg,\_,\_)$} is said to point to non-$\scall{}{}{}$ instruction $i$ in $A$ iff
  \[
    \reg(\pcreg) = ((\_,\_),\_,\eaddr,\aaddr) \tand \aaddr \in A
  \]
and
\[
  \decInstr{\ms(\aaddr)} = i
\]
\end{definition}
